### 2022-04-26 paper/Chapters/Evaluation.tex
Changes from feedback
Almost done

      \legend{Ideal,CPU stressed,GPU stressed,Both stressed}
    \end{axis}
  \end{tikzpicture}
  \caption[Color Delay Data]{Time for client to render update to the screen. Values over 250ms push the usability of the system. n=400.}
  \label{fig:ColorDelay}
\end{figure}

@@

\begin{figure}[!b]
  \centering
  \begin{subfigure}{1\textwidth}
    \centering
    \includegraphics[width=.9\linewidth]{Figures/realworld/kicad}
  \end{subfigure}
  \begin{subfigure}{1\textwidth}
    \centering
    \includegraphics[width=.5\linewidth]{Figures/realworld/kicadstats}
  \end{subfigure}
  \caption[Streaming Electronics Design software]{Working on the PCB for this thesis using KiCad.}
  \label{fig:RealWorldKicad}
\end{figure}

While the testing conducted in the previous two sections provide an overview of how each application performs under controlled conditions, testing in the real world provides better insight into how a user may experience the final product.
Unfortunately, there are many limitations in how testing can be conducted in the real world.
First and foremost, due to the closed nature of of the existing solutions, collecting data while using them in real-world scenarios is impossible while leveraging the tools from the previous sections.
Because of the reliance on using exact and repeatable testing conditions, a dynamic test of each application is much more difficult to conduct without direct access to the performance of the program, all data that could be collected otherwise would amount to quantitative data subject to interpretation.
However, because of the logging tools that were developed in Section \ref{sec:DevelopingTestingAndMeasurementTools}, it is possible to collect data from the forked version of moonlight that shows the performance of the application over an entire streaming session.
While it is impossible to predict and exhaustively test what the user may try to do with the final product, it is possible to test common use cases and evaluate whether the streaming experience is satisfactory.

@@

\begin{lstlisting}[style=plaintext,title=Statistics recorded while streaming KiCad (Figure \ref{fig:RealWorldKicad})]
Global Video Stats
----------------------------------------------------------
Incoming frame rate from network: 61.23 FPS
Decoding frame rate: 61.23 FPS
Rendering frame rate: 61.23 FPS
Frames dropped by your network connection: 0.00%
Average network latency: 1 ms (variance: 0 ms)
Average decoding time: 4.24 ms
Average rendering time (including monitor V-sync latency): 0.06 ms
Total dropped frames: 0
\end{lstlisting}

@@

@@

@@

@@

Finally, Moonlight proves to be a high-performant solution that isn't limited by the host's CPU or GPU being under stress.
Each test resulted in highly similar results, and while it does on average have slightly higher response times compared to RDP (Figures \ref{fig:InputDelay} and \ref{fig:ColorDelay}), it only falls behind by 5-10ms -- quicker than the blink of an eye.
By not dropping any frames, and numerically proving it's ability to keep the stream above 60 frames per second, Moonlight proves to be a great solution for streaming demanding applications to a remote client without compromising its usability.

>>>>

      \legend{Ideal,CPU stressed,GPU stressed,Both stressed}
    \end{axis}
  \end{tikzpicture}
  \caption[Color Delay Data]{Time for client to render update to the screen. Values over 250ms indicate a poorly performing system. n=400.}
  \label{fig:ColorDelay}
\end{figure}

@@

While the testing conducted in the previous two sections provide an overview of how each application performs under controlled conditions, testing in the real world provides better insight into how a user may experience the final product.
Unfortunately, there are many limitations in how testing can be conducted in the real world.
First and foremost, due to the closed nature of of the existing solutions, collecting data while using them in real-world scenarios is impossible while leveraging the tools from the previous sections.
Because of the reliance on using exact and repeatable testing conditions, a dynamic test of each application is much more difficult to conduct without direct access to the performance of the program, all data that could be collected otherwise would amount to quantitative data subject to interpretation.
However, because of the logging tools that were developed in Section \ref{sec:DevelopingTestingAndMeasurementTools}, it is possible to collect data from the forked version of Moonlight that shows the performance of the application over an entire streaming session.
While it is impossible to predict and exhaustively test what the user may try to do with the final product, it is possible to test common use cases and evaluate whether the streaming experience is satisfactory.

Each of the following subsections aims to represent a different use case that may be encountered in the real world.
First, the project is tested with a CAD application in Section \ref{subsec:RealWorldKiCad}, representing precise graphical design using software that may struggle to run on portable hardware.
Then, to represent a programming environment while utilizing the power of the host, the project is tested while training an AI model in Section \ref{subsec:RealWorldAI}.
Then, the project is tested while using Blender to edit and render a 3D scene simultaneously to represent artistic workloads and GPU accelerated rendering in Section \ref{subsec:RealWorldBlender}.
Finally, to represent an all around stressful situation for the host, the project is tested while developing a level for a video game while inspecting it in-game in Section \ref{subsec:RealWorldVideoGame}.

\subsection{CAD}\label{subsec:RealWorldKiCad}

\begin{figure}[t]
  \centering
  \begin{subfigure}{1\textwidth}
    \centering
    \includegraphics[width=.9\linewidth]{Figures/realworld/kicad}
  \end{subfigure}
  \begin{subfigure}{1\textwidth}
    \centering
    \includegraphics[width=.5\linewidth]{Figures/realworld/kicadstats}
  \end{subfigure}
  \caption[Streaming Electronics Design software]{Working on the PCB for this thesis using KiCad.}
  \label{fig:RealWorldKicad}
\end{figure}

@@

\vspace{3mm} % Get the header of the block onto the next page. This can be removed if formatting changes
\begin{lstlisting}[style=plaintext,title=Statistics recorded while streaming KiCad (Figure \ref{fig:RealWorldKicad})]
Global Video Stats
----------------------------------------------------------
Incoming frame rate from network: 61.23 FPS
Decoding frame rate: 61.23 FPS
Rendering frame rate: 61.23 FPS
Frames dropped by your network connection: 0.00%
Average network latency: 1 ms (variance: 0 ms)
Average decoding time: 4.24 ms
Average rendering time (including monitor V-sync latency): 0.06 ms
Total dropped frames: 0
\end{lstlisting}

@@

\subsection{AI Training}\label{subsec:RealWorldAI}

@@

\subsection{3D Rendering}\label{subsec:RealWorldBlender}

@@

\subsection{Video Game Development}\label{subsec:RealWorldVideoGame}

@@

Finally, Moonlight proves to be a high-performant solution that isn't limited by the host's CPU or GPU being under stress.
Each test resulted in highly similar results, and while it does on average have slightly higher response times compared to RDP (Figures \ref{fig:InputDelay} and \ref{fig:ColorDelay}), it only falls behind by 5-10ms -- quicker than the blink of an eye.
Moonlight also provided an uncompromising experience throughout each of the real world use cases.
By dropping zero frames across seven of the eight tests conducted for this thesis, and only 0.06\% of frames on the final test, and numerically proving it's ability to keep the stream above 60 frames per second in nearly every situation, Moonlight proves to be a great solution for streaming demanding applications to a remote client without compromising its usability.
